\section{Experience}

%\cventry{xxx--xxx}{title}{company, city, country}{}{}{description}

\cventry{2025--current}{Deputy CEO}{Karband Eng. Co., Alborz, Iran}{}{}{I lead initiatives in Geospatial AI and Unmanned Ground Vehicles (UGVs) — developing intelligent systems that move, sense, and learn from the world around them. My work bridges robotics, spatial data, and applied machine learning to create technologies that operate seamlessly in real environments.
%
Alongside this, I'm passionate about AI education for youth. I believe that teaching kids to think in systems — to design, build, and experiment — is key to nurturing a generation capable of shaping technology with creativity and purpose.
%
At the heart of my work is a simple idea: technology should serve both intelligence and integrity. Whether through autonomous robots, spatial analytics, or educational projects, I aim to help build an ecosystem of AI that is local, sustainable, and deeply human in its intention.}

\cventry{2022--2025}{Staff Software Engineer}{EarthDaily Analytics, Vancouver, Canada}{}{}{EarthDaily observes, verifies, \& predicts changes to the Earth\'s surface to help people understand \& take action.}

\cventry{2022}{Senior Machine Learning Engineer (Computer Vision)}{Vivid Machines, Toronto, Canada}{}{}{Smart technology to help fruit and vegetable farmers optimize quality and yield.}

\cventry{2020--2022}{Vice President, Data Science}{Savormetrics Inc., Mississauga, Canada}{}{}{Deep Learning + Food Inspection = Increasing Profits. Reducing Waste. Improving Customer Satisfaction.}

\cventry{2019--2020}{Lead Data Scientist}{Betterview Marketplace, San Diego, USA}{}{}{Design, development, and deployment of a deep learning framework that consumes aerial images and other types of data relevant to the insurance industry and produces property insights.}

\cventry{2016--2019}{Senior Scientific Developer}{Fio Corporation, Toronto, Canada}{}{}{Design, development, and deployment of a learning-enabled machine vision system that visually identifies and analyzes rapid diagnostics tests (rdt) for infectious diseases such as HIV, Malaria, Dengue, Zika, and others. At inference time, the ML models are run on an android device with limited network and power access. Therefore, battery usage optimization and tolerance to long periods of disconnectivity were essential considerations. Traceability management for data and models was a vital component of this work due to national and international regulatory requirements.}

\cventry{2015--2016}{Research Scientist}{Intellijoint Surgical, Waterloo, Canada}{}{}{Extensions of the capabilities of a monocular infrared tracking system that was a component within the surgical navigation product that utilized machine vision to carry out and confirm geometrical measurements in-vivo. Also, worked on the inertial data that was produced by the system for validation and augmentation. Parameter estimation using least mean square and Levenberg-Marquardt cost function minimization.}

\cventry{2009--2015}{Researcher}{Imaging Group, Epson Canada Limited, Toronto, Canada}{}{}{Research and development on future products and concepts in the fields of visual inspection, symbology detection, 3d object detection and pose estimation, camera calibration (monocular, stereo, and depth/range), augmented and virtual reality, 3d scan/display systems (stereo, time-of-flight, structured light projection, and other depth sensors), depth processing (including bilateral upsampling, filtering, and registration and fusion of multiple depth and flat cameras using different variations of iterative closest point - icp), head-mounted displays, and robotics. Stochastic optimization in the presence of outliers using RANSAC and robustified cost minimization.}

\cventry{2001--2004}{Process Control Engineer}{Karband Eng. Co., Alborz, Iran}{}{}{Design, implementation and erection of PLC-based control systems for medium-sized machinery in pipe and profile production plants.}

\cventry{1998--2001, 2004--2009}{Research Assistant}{University of Manitoba, Telecommunications Research Laboratories (TRLabs) Winnipeg and Biomechanics Laboratory, Sharif University of Technology}{}{}{Network optimization, earthquake damage detection using satellite/aerial imagery, human gait analysis, 3d surface reconstruction, color image watermarking and data-hiding, visual encryption, image compression, color transfer, grayscale image colorization, computational photography, fuzzy clustering, skin detection, and pornography classification. Fuzzy modelling of multi-layer systems, especially within the field of pattern recognition, using Bayesian models.}